A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-06 paper.tex
just in case

\begin{proof}
We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
\begin{align*}
& (t \varsigma, \rho, t \phi, A_{1,0}) \\
& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
\end{align*}
This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
\begin{align*}
\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
\end{align*}

The next step is to decompose the $(1,1)$ form $\psi$ as
\[
\psi = \omega \Lambda \psi + \psi_{\perp}
\]
where $\Lambda \psi_{\perp} = 0$.

\chris{I just made the following attempt}
\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC_{\rm Dol} \times \RR^2_{\mr{dR}}, B\fg_{\Hod}\right)$. Moreover, this equivalence is $\spin(2;\RR) \times \spin(2;\RR)$-equivariant.
\end{theorem}

@@

This theory admits a unique twist:
\begin{itemize}
 \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.  There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
\end{itemize}

@@

In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.  The classification of orbits includes the rank of this map.
\begin{itemize}
 \item Rank 1.  In this case $Q$ is minimal, with 2 invariant directions.  Such supercharges come from the $\mc N=2$ supersymmetry algebra.  They admit the twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $A$-twist.  Rank 2 supercharges are topological.  A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.  The $G_R = \Spin(4;\RR)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.  We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.  The A-twist admits the twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$. and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $B$-twist.  The other topological orbit admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  This twist is only $\ZZ/2\ZZ$-graded
\end{itemize}

>>>>

%\begin{proof}
%We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
%\begin{align*}
%& (t \varsigma, \rho, t \phi, A_{1,0}) \\
%& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
%\end{align*}
%This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
%\begin{align*}
%\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
%%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
%&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
%\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
%\end{align*}
%
%The next step is to decompose the $(1,1)$ form $\psi$ as
%\[
%\psi = \omega \Lambda \psi + \psi_{\perp}
%\]
%where $\Lambda \psi_{\perp} = 0$. 
%
%\end{proof}

\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC_{\rm Dol} \times \RR^2_{\mr{dR}}, B\fg_{\Hod}\right)$. Moreover, this equivalence is $\spin(2;\RR) \times \spin(2;\RR)$-equivariant.
\end{theorem}

@@

This theory admits a unique twist up to equivalence:
\begin{itemize}
 \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.  There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
\end{itemize}

@@

In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.  The classification of orbits includes the rank of this map.
\begin{itemize}
 \item Rank 1.  
 In this case $Q$ is minimal, with 2 invariant directions.  
 Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence.
They admit a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading defined by a homomorphism $\alpha \colon \U(1) \to G_R$.
 \item Rank 2. Such supercharges are topological.  
A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.  
The $G_R = \Spin(4;\CC)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.  
We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.
\begin{enumerate}
\item
An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$. and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
\item
A $B$-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
This twist is only $\ZZ/2\ZZ$-graded
\end{enumerate}
\end{itemize}
